Rscript -e "rmarkdown::render('Inference.Rmd')"

**Optional primary_site**
"Adipose Tissue"             "Muscle"                     "Blood Vessel"               "Heart"                      "Ovary"                     
"Uterus"                     "Breast"                     "Salivary Gland"             "Brain"                      "Adrenal Gland"             
"Thyroid"                    "Lung"                       "Pancreas"                   "Esophagus"                  "Stomach"                   
"Skin"                       "Colon"                      "Small Intestine"            "Prostate"                   "Testis"                    
"Nerve"                      "Spleen"                     "Pituitary"                  "Blood"                      "Vagina"                    
"Liver"                      "Kidney"                     "Bladder"                    "Fallopian Tube"             "Cervix Uteri"              
"Bone Marrow"                "White blood cell"           "Sympathetic Nervous System" "Endometrium"                "Cervix"                    
"Soft tissue,Bone"           "Thymus"                     "Lining of body cavities"    "Bile duct"                  "Thyroid Gland"             
"Head and Neck region"       "Rectum"                     "Lymphatic tissue"           "Adrenal gland"              "Paraganglia"               
"Eye"

**Optional sample_type**
"Normal Tissue"                                     "Cell Line"                                        
"Primary Blood Derived Cancer - Peripheral Blood"   "Primary Blood Derived Cancer - Bone Marrow"       
"Recurrent Blood Derived Cancer - Bone Marrow"      "Recurrent Blood Derived Cancer - Peripheral Blood"
"Post treatment Blood Cancer - Bone Marrow"         "Post treatment Blood Cancer - Blood"              
"Primary Solid Tumor"                               "Recurrent Solid Tumor"                            
"Solid Tissue Normal"                               "Metastatic"                                       
"Primary Tumor"                                     "Recurrent Tumor"                                  
"Additional - New Primary"                          "Additional Metastatic"  

```{r}
num_samples = 100L # How many samples do you want to generate
primary_site = "Breast"
sample_type = "Primary Tumor"
```

Load packages
```{r}
library(keras)
library(abind)
library(tensorflow)
library(Rtsne)
library(ggplot2)
library(magrittr)
load("other.Rdata")
generator <- load_model_tf("generator")
```

```{r}
text_vectorization <- layer_text_vectorization(max_tokens = max_tokens + 2, # 2 contain "" and "[UNK]"
                                               standardize = NULL,
                                               split = function(x){tf$strings$split(x, sep = "/")},
                                               output_mode = "int",
                                               output_sequence_length = 2,
                                               name = "text_vectorization")
text_vectorization$set_vocabulary(vocabulary)
  
denormalize <- function(samples){
  max <- tf$expand_dims(max, axis = 0L)
  min <- tf$expand_dims(min, axis = 0L)
  samples <- samples * (max - min) + min
  sum <- tf$reduce_sum(samples, axis = -1L, keepdims = T)
  samples <- samples / sum * library_size
  return(samples)
}

label2index <- function(samples_labels){
  samples_labels <- tf$strings$join(list(samples_labels$primary_site, samples_labels$sample_type), separator="/")
  samples_labels <- text_vectorization(samples_labels)
  return(samples_labels)
}

generate = function(num_samples, samples_labels){
  c(primary_site, sample_type) %<-% samples_labels
  samples_labels <- data.frame(primary_site=rep(primary_site, num_samples), sample_type=rep(sample_type, num_samples))
  samples_labels <- label2index(samples_labels)
  
  noise <- tf$random$normal(shape = c(as.integer(num_samples), 128L))
  generated_samples <- generator$predict(list(noise, samples_labels))
  generated_samples <- denormalize(generated_samples) %>% as.array()
  colnames(generated_samples) <- Ensembl_ID
  return(generated_samples)
}
```

```{r}
generated_samples <- generate(num_samples = num_samples, samples_labels = list(primary_site, sample_type))
save(generated_samples, file = "generated_samples.Rdata")
```
